---
title: "COVID19 vaccine benefit risk assessment - input data overview"
output: html_document
params:
  params: NA
  countries: NA
  age_groups_benefits: NA
  vaccines: NA
  variants: NA
  conditions_per_vaccine: NA
  age_groups_per_condition: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
require(tidyverse)
```

## Countries

`r paste0(params$countries, collapse = ', ')`

## Vaccines

`r paste0(params$vaccines, collapse = ', ')`

## Variants

`r paste0(params$variants, collapse = ', ')`

## Age groups benefit analysis

`r paste0(params$age_groups_benefits, collapse = ', ')`

## Conditions analysed per vaccine

```{r, echo = FALSE}
knitr::kable(params$conditions_per_vaccine)
```

## Age groups by condition

```{r, echo = FALSE}
knitr::kable(params$age_groups_per_condition)
```

## Analysis window

Start: `r format(params$params$timewindow[1], '%B %d, %Y')`<br>
End: `r format(params$params$timewindow[2], '%B %d, %Y')`


## Parameters risk

```{r, echo = FALSE}
knitr::kable(params$params$param_risk)
```

## Parameters vaccine efficiency

```{r, echo = FALSE}
knitr::kable(params$params$param_ve %>% 
    pivot_longer(cols = -c(vaccine, dose, variant, against, parameter),
                names_to = 'scenario',
                values_to = 'value') %>%
    pivot_wider(names_from = parameter,
                values_from = value)
               )
```

